Combined effects of protein expression variance and correlation on multicomponent systems

### 2020-03-18 Manuscript/Manuscript.Rmd
.

```{r normalization, include=FALSE}
protImpute <- pepTidy %>% 
  group_by(peptide,run) %>% 
  mutate(intensity = intensity / intensity[label == "126"]) %>%
  ungroup() %>%
  filter(run != "ctrl", condition != "ctrl") %>%
  dplyr::filter(abs((intensity)) < 2*sd((pepTidy$intensity), na.rm = T)) %>%
  group_by(cell, run, label, condition, Uniprot) %>% 
  summarise(abundance = mean(intensity, na.rm = T)) %>% ungroup() %>%
  group_by(Uniprot) %>%
  mutate(abundance = abundance / mean(abundance, na.rm = T)) %>% 
  filter(n() > 15) %>% # comment out if using KNN
  group_by(cell) %>% 
  mutate(abundance = abundance / mean(abundance, na.rm = T)) %>% 
  ungroup() %>% 
  dplyr::select(cell, Uniprot, abundance) %>% 
  spread(cell, abundance)
  # spread(cell, abundance) %>%
  # kNN(data = ., k = 1, impNA = TRUE) %>% as_tibble() %>% dplyr::select(Uniprot:e_131_80)

>>>>

```{r normalization, include=FALSE}
protImpute <- pepTidy %>% 
  group_by(peptide,run) %>% 
  mutate(intensity = intensity / intensity[label == "126"]) %>%
  ungroup() %>%
  filter(run != "ctrl", condition != "ctrl") %>%
  dplyr::filter(abs((intensity)) < 2*sd((pepTidy$intensity), na.rm = T)) %>%
  group_by(cell, run, label, condition, Uniprot) %>% 
  summarise(abundance = mean(intensity, na.rm = T)) %>% ungroup() %>%
  group_by(Uniprot) %>%
  mutate(abundance = abundance / mean(abundance, na.rm = T)) %>% 
  # filter(n() > 15) %>% # comment out if using KNN
  group_by(cell) %>% 
  mutate(abundance = abundance / mean(abundance, na.rm = T)) %>% 
  ungroup() %>% 
  dplyr::select(cell, Uniprot, abundance) %>% 
  spread(cell, abundance)
  spread(cell, abundance) %>%
  kNN(data = ., k = 1, impNA = TRUE) %>% as_tibble() %>% dplyr::select(Uniprot:e_131_80)
